Meta-analysis

### 2020-01-02 04_Prep_data.Rmd
Merge two tables to one and, clarify explaination

@@

## Standardising sample variance

The type of variance needs to be standardised between trials and treatments for the meta-analysis.

```{r variance_types}
# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing == 0.75) %>%
   group_by(trial_ref, location, Y_error_type) %>%
   summarise(tebuconazole_trts = length(Y_error_type))

# Trials using propiconazole
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole",
          row_spacing == 0.75) %>%
   group_by(trial_ref, location, Y_error_type) %>%
   summarise(propiconazole_trts = length(Y_error_type))
```

The experiment summaries report either standard deviation, least square differences or no error term (`NA`). Below we will convert LSD and standard deviation to sample variance

>>>>

## Set environment and import data

@@

## Standardising sample variance  
Meta-analyses use variance from the data to calculate the effect sizes. The type of variance needs to be the same across all the data incorporated in the meta-analysis.

We are narrowing the meta-analysis to only include demethylation inhibitors, tebuconazole and propiconazole. Within studies which have used these fungicides, what type of error was reported?

```{r variance_types}
# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole",
         row_spacing == 0.75) %>%
   group_by(trial_ref, location, Y_error_type, fungicide_ai) %>%
   summarise(tebuconazole_trts = length(Y_error_type))%>%
   arrange(Y_error_type)

The experiment summaries report either standard deviation, least square differences or no error term (`NA`). Below we will convert LSD and standard deviation to sample variance. In addition, we need to impute variances for the trials which did not report any form of variance (`NA`).
